---
title: "Heatmaps Phi Bounds and Cole's C vs. Yule's Q vs. Phi"
output: 
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: inline
---

```{r packages, include = FALSE}
library(remotes)
library(BCor)
library(patchwork)
library(psych)
library(tidyr)
library(dplyr)
library(ggplot2)
library(mvtnorm)
library(here)
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE, echo = TRUE)
```

# Function: Compare coefficient1 with coefficient2 by using a heatmap

-   coefficient1: Coefficient that gets evaluated, i.e. whose values get displayed in the heatmap
-   coefficient2.inv: Coefficient that gets fixed and used to create contingency tables for varying marginal distributions
-   level: Level at which coefficient2 gets fixed
-   xlim, ylim: range of PA and PB as a vector. Recommendation: use c(0.01, 0.99) but don't include 0 or 1. This will produce errors.
-   xlab, ylab: axis description with strings
-   PA: Marginal probability for event A (row 1 in contingency table)
-   PB: Marginal probability for event B (column 1 in contingency table)

```{r plot_contour_binary}
plot_contour_binary <- function(coefficient1, coefficient2.inv, level, xlim, ylim, grid, xlab, ylab, bins){
  # function yielding the value for coefficient1 given the contingency table which is determined by coefficient2.inv, PA and PB
  f <- function(coefficient1, coefficient2.inv, PA, PB){
    as.numeric(coefficient1(coefficient2.inv(level, c(PA, 1 - PA, PB, 1 - PB)), alpha = FALSE))
  }
  
  PA <- seq(xlim[1], xlim[2], length.out = grid)
  PB <- seq(ylim[1], ylim[2], length.out = grid)
  data <- expand_grid(x = PA, y = PB)
  z <- rep(NA,grid^2)
  for (i in 1:grid){
    for (j in 1:grid){
      z [(i-1)*grid+j]<- f(coefficient1, coefficient2.inv, PA[i], PB[j])
    }}
  data <- mutate(data, z) 
  
  labels <- rep("",bins+1)
  
  addlabels <- seq(from=-1,to=1,length.out=11)
  
  addlabelsat <- seq(from=1, to=bins+1,length.out=11)
  
  labels[addlabelsat] <- addlabels
  
  g <- ggplot(data, aes(x = x, y = y, fill = z)) +
    geom_tile()+
    scale_fill_stepsn(n.breaks = bins, colors = hcl.colors(20, "Spectral"), limits = c(-1, 1), labels = labels)+
    guides(fill = guide_colourbar(title = NULL, ticks = FALSE, barheight = 10))+
    xlab(xlab) +
    ylab(ylab)
  
  # "Green-Brown" or "Blue-Red 3" instead of "Spectral" are colorblind-safe, but for smaller ranges of values do not distinguish as well

  g
}
plot_contour_trivial <- function(level, xlim, ylim, grid, xlab, ylab, bins){
  # function yielding a trivial heatmap with value 'level', i.e. the whole square in one color
  f <- function(PA, PB){level}
  
  PA <- seq(xlim[1], xlim[2], length.out = grid)
  PB <- seq(ylim[1], ylim[2], length.out = grid)
  data <- expand_grid(x = PA, y = PB)
  z <- rep(NA,grid^2)
  for (i in 1:grid){
    for (j in 1:grid){
      z [(i-1)*grid+j]<- f(PA[i], PB[j])
    }}
  data <- mutate(data, z) 
  
  labels <- rep("",bins+1)
  
  addlabels <- seq(from=-1,to=1,length.out=11)
  
  addlabelsat <- seq(from=1, to=bins+1,length.out=11)
  
  labels[addlabelsat] <- addlabels
  
  g <- ggplot(data, aes(x = x, y = y, fill = z)) +
    geom_tile()+
    scale_fill_stepsn(n.breaks = bins, colors = hcl.colors(20, "Spectral"), limits = c(-1, 1), labels = labels)+
    guides(fill = guide_colourbar(title = NULL, ticks = FALSE, barheight = 10))+
    xlab(xlab) +
    ylab(ylab)
  
  # "Green-Brown" or "Blue-Red 3" instead of "Spectral" are colorblind-safe, but for smaller ranges of values do not distinguish as well

  g
}
```

## Including Plots

Bounds for Phi

```{r}
gridsize <- 250
plot_contour_binary(Phi, Cole.inv, -1, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() + theme_minimal(base_size = 15) + theme(
  axis.text.x = element_text(color="black"),
  axis.text.y = element_text(color="black"),
  axis.ticks = element_line(color = "black")
) + plot_contour_binary(Phi, Cole.inv, 1, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() + theme_minimal(base_size = 15) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_layout(guides = 'collect', ncol = 2)
ggsave(filename = here("application/plots/phi_bounds.pdf"), width = 200, height = 90, device = "pdf", units = "mm")
```


Heatmaps with Cole as the coefficient to be set and comparison with Cole, YuleQ and Phi

```{r heatmaps_cole}
gridsize <- 250
adj_width <- 50
adj_height <- 95
base_size <- 18
plot_contour_trivial(0.3, c(0.01,0.99), c(0.01,0.99), 10, "P(A)", "P(B)", 40) + coord_fixed() + 
  theme_minimal(base_size = base_size) + ggtitle("Cole's C") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.text.y = element_text(color="black"),
  axis.ticks = element_line(color = "black")
) + plot_contour_binary(YuleQ, Cole.inv, 0.3, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed()  +
  theme_minimal(base_size = base_size) + ggtitle("Yule's Q") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_contour_binary(Phi, Cole.inv, 0.3, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() +
  theme_minimal(base_size = base_size) + ggtitle("Phi Coefficient") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_layout(guides = 'collect', ncol = 3)
ggsave(filename = here("application/plots/cole_comparison_03.pdf"), height = 200 - adj_height, width = (1+sqrt(5))/2*200 - adj_width, device = "pdf", units = "mm")

plot_contour_trivial(0.7, c(0.01,0.99), c(0.01,0.99), 10, "P(A)", "P(B)", 40) + coord_fixed() + 
  theme_minimal(base_size = base_size) + ggtitle("Cole's C") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.text.y = element_text(color="black"),
  axis.ticks = element_line(color = "black")
) + plot_contour_binary(YuleQ, Cole.inv, 0.7, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() +
  theme_minimal(base_size = base_size) + ggtitle("Yule's Q") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_contour_binary(Phi, Cole.inv, 0.7, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() +
  theme_minimal(base_size = base_size) + ggtitle("Phi Coefficient") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_layout(guides = 'collect', ncol = 3)
ggsave(filename = here("application/plots/cole_comparison_07.pdf"), height = 200 - adj_height, width = (1+sqrt(5))/2*200 - adj_width, device = "pdf", units = "mm")

plot_contour_trivial(-0.3, c(0.01,0.99), c(0.01,0.99), 10, "P(A)", "P(B)", 40) + coord_fixed() + 
  theme_minimal(base_size = base_size) + ggtitle("Cole's C") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.text.y = element_text(color="black"),
  axis.ticks = element_line(color = "black")
) + plot_contour_binary(YuleQ, Cole.inv, -0.3, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() +
  theme_minimal(base_size = base_size) + ggtitle("Yule's Q") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_contour_binary(Phi, Cole.inv, -0.3, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() +
  theme_minimal(base_size = base_size) + ggtitle("Phi Coefficient") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_layout(guides = 'collect', ncol = 3)
ggsave(filename = here("application/plots/cole_comparison_-03.pdf"), height = 200 - adj_height, width = (1+sqrt(5))/2*200 - adj_width, device = "pdf", units = "mm")

plot_contour_trivial(-0.7, c(0.01,0.99), c(0.01,0.99), 10, "P(A)", "P(B)", 40) + coord_fixed() + 
  theme_minimal(base_size = base_size) + ggtitle("Cole's C") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.text.y = element_text(color="black"),
  axis.ticks = element_line(color = "black")
) + plot_contour_binary(YuleQ, Cole.inv, -0.7, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() +
  theme_minimal(base_size = base_size) + ggtitle("Yule's Q") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_contour_binary(Phi, Cole.inv, -0.7, c(0.01,0.99), c(0.01,0.99), gridsize, "P(A)", "P(B)", 40) + coord_fixed() +
  theme_minimal(base_size = base_size) + ggtitle("Phi Coefficient") + theme(plot.title = element_text(hjust = 0.5, size = 18)) + theme(
  axis.text.x = element_text(color="black"),
  axis.ticks.x = element_line(color = "black"),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
) + plot_layout(guides = 'collect', ncol = 3)
ggsave(filename = here("application/plots/cole_comparison_-07.pdf"), height = 200 - adj_height, width = (1+sqrt(5))/2*200 - adj_width, device = "pdf", units = "mm")
```


