---
title: "Interdependence between Drugs"
geometry: "left=2cm,right=3cm,top=2cm,bottom=2cm"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE, echo = TRUE, fig.width = 10, fig.height = 8)
```

```{r packages}
library(BCor) # Install via remotes::install_github("jan-lukas-wermuth/BCor") if not done yet
# Package names
packages <- c("tidyverse",
              "here",
              "mvtnorm",
              "readxl", # import from Excel
              "formatR", # 'double'-pipe
              "patchwork", # plot arrangement
              "Cairo") # save pdf (only necessary to have \phi properly illustrated with ggsave). This may be complicated to install. If you are on Mac, make sure to have XQuartz installed.

# Install packages
# Loop: checks if packages are already installed. If not, they will be installed.
# Otherwise, they will be updated.
for(i in packages){
  if(!require(i, character.only = T)){
    install.packages(i, dependencies = T)
    require(i, character.only = T)
  }
}
```

# Preparation work

Load data in terms of p, q and r. The structure of pqr_arr is the following: The first dimension marks the first drug and the second dimension the second drug. The third dimension marks p, q or r. p always refers to the relative consumption frequency of the first drug in the comparison and q to the relative consumption frequency of the second drug in the comparison. r denotes the joint relative consumption frequency.

```{r data}
load(here("application/data_pqr/pqr_arr.RData"))
```

Load functions:

1. comparison_binary: Function yielding a list containing Cole's C, Yule's Q and Phi.
2. plot_contour_matrix: Function creating heatmap with rows/columns ordered according to skewness of the marginal distribution.

```{r functions}
# Insert variable1 and variable2 as strings, e.g. "MET"
comparison_binary <- function(variable1, variable2){
  phi <- as.numeric(Phi(pqr_arr[variable1, variable2, c("p", "q", "r")], alpha = FALSE))
  cole <- as.numeric(Cole(pqr_arr[variable1, variable2, c("p", "q", "r")], alpha = FALSE))
  yule <- as.numeric(YuleQ(pqr_arr[variable1, variable2, c("p", "q", "r")], alpha = FALSE))
  result <- list("Phi" = phi, "Cole's C" = cole, "Yule's Q" = yule)
  return(result)
}
plot_contour_matrix <- function(mat, xlab, ylab, bins){
  drug_d_sorted <- as.factor(c("ALC", "MAR", "CIG", "AMP", "TRQ", "NAR", "LSD", "PSY", "SED", "MDM", "COK", "CRA", "MET", "HER")) # drugs sorted according to their marginal relative consumption frequencies
  drug_d_sorted_desc <- as.factor(rev(drug_d_sorted))
  
  data <- expand_grid(x = drug_d_sorted, y = drug_d_sorted_desc)

  z <- rep(NA,dim(mat)[1]^2)
  for (i in 1:dim(mat)[1]){
    for (j in 1:dim(mat)[1]){
      z[(i-1)*dim(mat)[1]+j]<- mat[j, i]
    }}
  
  data <- mutate(data, z) 
  
  labels <- rep("",bins+1)
  
  addlabels <- seq(from=-1,to=1,length.out=11)
  
  addlabelsat <- seq(from=1, to=bins+1,length.out=11)
  
  labels[addlabelsat] <- addlabels
  
  g <- ggplot(data, aes(x = fct_inorder(x), y = fct_inorder(y), fill = z)) +
    geom_tile() +
    scale_fill_stepsn(n.breaks = bins, colors = hcl.colors(20, "Spectral"), limits = c(-1, 1), labels = labels) +
    guides(fill = guide_colourbar(title = NULL, ticks = FALSE, barheight = 10)) +
    xlab(xlab) +
    ylab(ylab)
  g
  # "Green-Brown" or "Blue-Red 3" instead of "Spectral" are colorblind-safe, but for smaller ranges of values do not distinguish as well
}
```

Create sorted (according to skewness) drug name vector in order to have the correlation (Cole's C, Yule's Q, Phi) matrices in the order in which the heatmap function needs it to be.

```{r drugs_sorted}
  drug_d_sorted <- c("ALC", "MAR", "CIG", "AMP", "TRQ", "NAR", "LSD", "PSY", "SED", "MDM", "COK", "CRA", "MET", "HER") # drugs sorted according to their marginal relative consumption frequencies
  drug_d_sorted_desc <- rev(drug_d_sorted)
```

Create correlation matrices (Cole's C, Yule's Q, Phi):

```{r matrices_correlation}
# Matrix 1: Phi ---------------------------------------------------------
df_phi <- matrix(NA, ncol = length(drug_d_sorted), nrow = length(drug_d_sorted))
colnames(df_phi) <- drug_d_sorted
rownames(df_phi) <- drug_d_sorted_desc
k <- 0

# Fill the data frame with the appropriate dependence measures for the appropriate comparison (sex vs. consumption of some drug)
for (i in drug_d_sorted_desc){
  k <- k + 1
  l <- 0
  for (j in drug_d_sorted){
    l <- l + 1
    df_phi[k, l] <- comparison_binary(i, j)[[1]]
  }
}

# Matrix 2: Cole's C ---------------------------------------------------------
df_cole <- matrix(NA, ncol = length(drug_d_sorted), nrow = length(drug_d_sorted))
colnames(df_cole) <- drug_d_sorted
rownames(df_cole) <- drug_d_sorted_desc
k <- 0

# Fill the data frame with the appropriate dependence measures for the appropriate comparison (sex vs. consumption of some drug)
for (i in drug_d_sorted_desc){
  k <- k + 1
  l <- 0
  for (j in drug_d_sorted){
    l <- l + 1
    df_cole[k, l] <- comparison_binary(i, j)[[2]]
  }
}


# Matrix 3: Yule's Q ---------------------------------------------------------
df_yule <- matrix(NA, ncol = length(drug_d_sorted), nrow = length(drug_d_sorted))
colnames(df_yule) <- drug_d_sorted
rownames(df_yule) <- drug_d_sorted_desc
k <- 0

# Fill the data frame with the appropriate dependence measures for the appropriate comparison (sex vs. consumption of some drug)
for (i in drug_d_sorted_desc){
  k <- k + 1
  l <- 0
  for (j in drug_d_sorted){
    l <- l + 1
    df_yule[k, l] <- comparison_binary(i, j)[[3]]
  }
}
```

\newpage

# Including Plots

Equipped with those three matrices, we can produce the respective heatmaps:

```{r heatmaps_absolute}
adj_width <- 50
adj_height <- 96
size <- 14

plot_contour_matrix(df_cole, "", "", 40) + coord_fixed() + theme_minimal(base_size = size) + 
    ggtitle("Cole's C") + theme(plot.title = element_text(hjust = 0.5)) + theme(
    axis.text.x = element_text(color="black", angle = 90),
    axis.text.y = element_text(color="black"),
    axis.ticks = element_line(color = "black"),
    legend.text = element_text(size = size)
  ) +
plot_contour_matrix(df_yule, "", "", 40) + coord_fixed() + theme_minimal(base_size = size) + 
    ggtitle("Yule's Q") + theme(plot.title = element_text(hjust = 0.5)) + theme(
    axis.text.x = element_text(color="black", angle = 90),
    axis.ticks.x = element_line(color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    legend.text = element_text(size = size)
  ) +
plot_contour_matrix(df_phi, "", "", 40) + coord_fixed() + theme_minimal(base_size = size) + 
    ggtitle("Phi Coefficient") + theme(plot.title = element_text(hjust = 0.5)) + theme(
    axis.text.x = element_text(color="black", angle = 90),
    axis.ticks.x = element_line(color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    legend.text = element_text(size = size)
) + plot_layout(guides = 'collect', ncol = 3)
ggsave(filename = here("application/plots/drugs_comparison.pdf"), height = 200 - adj_height, width = (1+sqrt(5))/2*200 - adj_width, device = "pdf", units = "mm")
```

\newpage

The last piece of code computes the confidence intervals of Cole's C, Phi and Yule's Q for all comparisons involving marijuana and meth.

```{r}
# Order drugs with respect to the frequency of use (except marijuana, which is our reference point)
  drugs_inference_sorted <- c("ALC", "CIG", "AMP", "TRQ", "NAR", "LSD", "PSY", "SED", "MDM", "COK", "CRA", "MET", "HER") # drugs sorted according to their marginal relative consumption frequencies
  drugs_inference_sorted_desc <- rev(drug_d_sorted)

marijuana_CI <- function(variable){ # function yielding all the estimates for Cole's C, Yule's Q and Phi as well as their confidence interval bounds
  C_est <- Cole(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = FALSE)[[1]]
  Phi_est <- Phi(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = FALSE)[[1]]
  Q_est <- YuleQ(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = FALSE)[[1]]
  marijuana_CI_C <- c(Cole(pqr_arr["MAR", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[2]], Cole(pqr_arr["MAR", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[3]])
  marijuana_CI_CZ <- c(Cole(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[2]], Cole(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[3]])
  marijuana_CI_Q <- c(YuleQ(pqr_arr["MAR", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[2]], YuleQ(pqr_arr["MAR", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[3]])
  marijuana_CI_QZ <- c(YuleQ(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[2]], YuleQ(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[3]])
  marijuana_CI_phi <- c(Phi(pqr_arr["MAR", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[2]], Phi(pqr_arr["MAR", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[3]])
  marijuana_CI_phiZ <- c(Phi(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[2]], Phi(pqr_arr["MAR", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MAR", variable, "n"])[[3]])
  res <- dplyr::tribble(~C_est, ~Phi_est, ~Q_est, ~marijuana_CI_C, ~marijuana_CI_CZ, ~marijuana_CI_Q, ~marijuana_CI_QZ, ~marijuana_CI_phi, ~marijuana_CI_phiZ,
                          #--|--|--|--|--|--|--|--|--
                          C_est, Phi_est, Q_est, marijuana_CI_C, marijuana_CI_CZ, marijuana_CI_Q, marijuana_CI_QZ, marijuana_CI_phi, marijuana_CI_phiZ)
  return(res)
}

Q_est <- NA
C_est <- NA
Phi_est <- NA
CI_lower_Q <- NA
CI_upper_Q <- NA
CI_lower_QZ <- NA
CI_upper_QZ <- NA
CI_lower_C <- NA
CI_upper_C <- NA
CI_lower_CZ <- NA
CI_upper_CZ <- NA
CI_lower_phi <- NA
CI_upper_phi <- NA
CI_lower_phiZ <- NA
CI_upper_phiZ <- NA
for (i in drugs_inference_sorted) {
  Q_est <- c(Q_est, marijuana_CI(i)$Q_est)
}
for (i in drugs_inference_sorted) {
  C_est <- c(C_est, marijuana_CI(i)$C_est)
} 
for (i in drugs_inference_sorted) {
  Phi_est <- c(Phi_est, marijuana_CI(i)$Phi_est)
} 
for (i in drugs_inference_sorted) {
  CI_lower_Q <- c(CI_lower_Q, marijuana_CI(i)$marijuana_CI_Q[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_Q <- c(CI_upper_Q, marijuana_CI(i)$marijuana_CI_Q[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_QZ <- c(CI_lower_QZ, marijuana_CI(i)$marijuana_CI_QZ[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_QZ <- c(CI_upper_QZ, marijuana_CI(i)$marijuana_CI_QZ[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_C <- c(CI_lower_C, marijuana_CI(i)$marijuana_CI_C[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_C <- c(CI_upper_C, marijuana_CI(i)$marijuana_CI_C[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_CZ <- c(CI_lower_CZ, marijuana_CI(i)$marijuana_CI_CZ[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_CZ <- c(CI_upper_CZ, marijuana_CI(i)$marijuana_CI_CZ[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_phi <- c(CI_lower_phi, marijuana_CI(i)$marijuana_CI_phi[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_phi <- c(CI_upper_phi, marijuana_CI(i)$marijuana_CI_phi[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_phiZ <- c(CI_lower_phiZ, marijuana_CI(i)$marijuana_CI_phiZ[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_phiZ <- c(CI_upper_phiZ, marijuana_CI(i)$marijuana_CI_phiZ[[1]][2])
}
# Need to omit the first entry (NA)
Q_est <- as.numeric(na.omit(Q_est))
C_est <- as.numeric(na.omit(C_est))
Phi_est <- as.numeric(na.omit(Phi_est))
CI_lower_Q <- as.numeric(na.omit(CI_lower_Q))
CI_upper_Q <- as.numeric(na.omit(CI_upper_Q))
CI_lower_QZ <- as.numeric(na.omit(CI_lower_QZ))
CI_upper_QZ <- as.numeric(na.omit(CI_upper_QZ))
CI_lower_C <- as.numeric(na.omit(CI_lower_C))
CI_upper_C <- as.numeric(na.omit(CI_upper_C))
CI_lower_CZ <- as.numeric(na.omit(CI_lower_CZ))
CI_upper_CZ <- as.numeric(na.omit(CI_upper_CZ))
CI_lower_phi <- as.numeric(na.omit(CI_lower_phi))
CI_upper_phi <- as.numeric(na.omit(CI_upper_phi))
CI_lower_phiZ <- as.numeric(na.omit(CI_lower_phiZ))
CI_upper_phiZ <- as.numeric(na.omit(CI_upper_phiZ))

data_Q <- data.frame(drugs = fct_inorder(drugs_inference_sorted),
                   Q_est = Q_est,
                   C_est = C_est,
                   Phi_est = Phi_est,
                   CI_lower_Q = CI_lower_Q,
                   CI_upper_Q = CI_upper_Q,
                   CI_lower_QZ = CI_lower_QZ,
                   CI_upper_QZ = CI_upper_QZ,
                   CI_lower_C = CI_lower_C,
                   CI_upper_C = CI_upper_C,
                   CI_lower_CZ = CI_lower_CZ,
                   CI_upper_CZ = CI_upper_CZ,
                   CI_lower_phi = CI_lower_phi,
                   CI_upper_phi = CI_upper_phi,
                   CI_lower_phiZ = CI_lower_phiZ,
                   CI_upper_phiZ = CI_upper_phiZ)
options(ggplot2.discrete.colour= c("blue", "red"))
ggplot(data_Q, aes(drugs, Q_est)) +
    geom_errorbar(aes(ymin = CI_lower_Q, ymax = CI_upper_Q, color = "Standard-CIs"), linewidth = 0.8, width = 0.33, position = position_nudge(x = 0.2)) +
    geom_errorbar(aes(ymin = CI_lower_QZ, ymax = CI_upper_QZ, color = "Fisher-CIs"), linewidth = 0.8, width = 0.3, position = position_nudge(x = 0.2)) +
    geom_errorbar(aes(ymin = CI_lower_C, ymax = CI_upper_C, color = "Standard-CIs"), linewidth = 0.8, width = 0.3, position = position_nudge(x = -0.2)) +
    geom_errorbar(aes(ymin = CI_lower_CZ, ymax = CI_upper_CZ, color = "Fisher-CIs"), linewidth = 0.8, width = 0.3, position = position_nudge(x = -0.2)) +
    geom_errorbar(aes(ymin = CI_lower_phi, ymax = CI_upper_phi, color = "Standard-CIs"), linewidth = 0.8, width = 0.3) +
    geom_errorbar(aes(ymin = CI_lower_phiZ, ymax = CI_upper_phiZ, color = "Fisher-CIs"), linewidth = 0.8, width = 0.3) +
    geom_point(aes(drugs, Q_est, shape = "Q"), size = 3, position = position_nudge(x = 0.2)) +
    geom_point(aes(drugs, C_est, shape = "C"), size = 3, position = position_nudge(x = -0.2)) +
    geom_point(aes(drugs, Phi_est, shape = "\u03D5"), size = 3) +
    labs(x = "Drugs",
         y = "Cole's C, Phi Coefficient, Yule's Q") +
    geom_hline(yintercept = c(0,1), linetype = "dashed", color = "grey", alpha = 0.5) +
    geom_vline(xintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5, 10.5, 11.5, 12.5), color = "grey", alpha = 0.5) +
    theme_classic(base_size = 15) + 
    theme(legend.text = element_text(size=15), legend.position = "bottom", axis.title=element_text(size=15)) +
    scale_shape_manual(values = c(15, 16, 17)) +
    scale_colour_discrete(name = "") +
    scale_shape_discrete(name = "", breaks = c("C", "\u03D5", "Q")) +
    ylim(0,1.06)


ggsave(filename = here("application/plots/QCPhi_application_inference.pdf"), height = 200, width = (1+sqrt(5))/2*200, device = cairo_pdf, units = "mm")


```

```{r}
# Same figure as above but only with Fisher-CIs
options(ggplot2.discrete.colour= c("blue", "red", "green4"))
ggplot(data_Q, aes(drugs, Q_est)) +
    geom_errorbar(aes(ymin = CI_lower_QZ, ymax = CI_upper_QZ), color = "black", linewidth = 0.8, width = 0.3, position = position_nudge(x = 0.2)) +
    geom_errorbar(aes(ymin = CI_lower_CZ, ymax = CI_upper_CZ), color = "black", linewidth = 0.8, width = 0.3, position = position_nudge(x = -0.2)) +
    geom_errorbar(aes(ymin = CI_lower_phiZ, ymax = CI_upper_phiZ), color = "black", linewidth = 0.8, width = 0.3) +
    geom_point(aes(drugs, Q_est, shape = "Q", color = "Q"), size = 3, position = position_nudge(x = 0.2)) +
    geom_point(aes(drugs, C_est, shape = "C", color = "C"), size = 3, position = position_nudge(x = -0.2)) +
    geom_point(aes(drugs, Phi_est, shape = "\u03D5", color = "\u03D5"), size = 3) +
    labs(x = "Drugs",
         y = "Cole's C, Phi Coefficient, Yule's Q") +
    geom_hline(yintercept = c(0,1), linetype = "dashed", color = "grey", alpha = 0.5) +
    geom_vline(xintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5, 10.5, 11.5, 12.5), color = "grey", alpha = 0.5) +
    theme_classic(base_size = 15) + 
    theme(legend.text = element_text(size=15), legend.position = "bottom", axis.title=element_text(size=15)) +
    scale_colour_manual(values = c("blue", "red", "yellow")) +
    scale_shape_manual(values = c(15, 16, 17)) +
    scale_colour_discrete(name = "", breaks = c("C", "\u03D5", "Q")) +
    scale_shape_discrete(name = "", breaks = c("C", "\u03D5", "Q")) +
    ylim(0,1.06)


ggsave(filename = here("application/plots/QCPhi_application_inference_final.pdf"), height = 200, width = (1+sqrt(5))/2*200, device = cairo_pdf, units = "mm")
```




```{r}
# Order drugs with respect to the frequency of use (except meth, which is our reference point)
  drugs_inference_sorted <- c("ALC", "MAR", "CIG", "AMP", "TRQ", "NAR", "LSD", "PSY", "SED", "MDM", "COK", "CRA", "HER") # drugs sorted according to their marginal relative consumption frequencies
  drugs_inference_sorted_desc <- rev(drug_d_sorted)

meth_CI <- function(variable){ # function yielding all the estimates for Cole's C, Yule's Q and Phi as well as their confidence interval bounds
  C_est <- Cole(pqr_arr["MET", variable, c("p", "q", "r")], alpha = FALSE)[[1]]
  Phi_est <- Phi(pqr_arr["MET", variable, c("p", "q", "r")], alpha = FALSE)[[1]]
  Q_est <- YuleQ(pqr_arr["MET", variable, c("p", "q", "r")], alpha = FALSE)[[1]]
  meth_CI_C <- c(Cole(pqr_arr["MET", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[2]], Cole(pqr_arr["MET", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[3]])
  meth_CI_CZ <- c(Cole(pqr_arr["MET", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[2]], Cole(pqr_arr["MET", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[3]])
  meth_CI_Q <- c(YuleQ(pqr_arr["MET", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[2]], YuleQ(pqr_arr["MET", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[3]])
  meth_CI_QZ <- c(YuleQ(pqr_arr["MET", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[2]], YuleQ(pqr_arr["MET", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[3]])
  meth_CI_phi <- c(Phi(pqr_arr["MET", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[2]], Phi(pqr_arr["MET", variable, c("p", "q", "r")], Fisher = FALSE, alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[3]])
  meth_CI_phiZ <- c(Phi(pqr_arr["MET", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[2]], Phi(pqr_arr["MET", variable, c("p", "q", "r")], alpha = 0.9, n = pqr_arr["MET", variable, "n"])[[3]])
  res <- dplyr::tribble(~C_est, ~Phi_est, ~Q_est, ~meth_CI_C, ~meth_CI_CZ, ~meth_CI_Q, ~meth_CI_QZ, ~meth_CI_phi, ~meth_CI_phiZ,
                          #--|--|--|--|--|--|--|--|--
                          C_est, Phi_est, Q_est, meth_CI_C, meth_CI_CZ, meth_CI_Q, meth_CI_QZ, meth_CI_phi, meth_CI_phiZ)
  return(res)
}

Q_est <- NA
C_est <- NA
Phi_est <- NA
CI_lower_Q <- NA
CI_upper_Q <- NA
CI_lower_QZ <- NA
CI_upper_QZ <- NA
CI_lower_C <- NA
CI_upper_C <- NA
CI_lower_CZ <- NA
CI_upper_CZ <- NA
CI_lower_phi <- NA
CI_upper_phi <- NA
CI_lower_phiZ <- NA
CI_upper_phiZ <- NA
for (i in drugs_inference_sorted) {
  Q_est <- c(Q_est, meth_CI(i)$Q_est)
}
for (i in drugs_inference_sorted) {
  C_est <- c(C_est, meth_CI(i)$C_est)
} 
for (i in drugs_inference_sorted) {
  Phi_est <- c(Phi_est, meth_CI(i)$Phi_est)
} 
for (i in drugs_inference_sorted) {
  CI_lower_Q <- c(CI_lower_Q, meth_CI(i)$meth_CI_Q[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_Q <- c(CI_upper_Q, meth_CI(i)$meth_CI_Q[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_QZ <- c(CI_lower_QZ, meth_CI(i)$meth_CI_QZ[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_QZ <- c(CI_upper_QZ, meth_CI(i)$meth_CI_QZ[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_C <- c(CI_lower_C, meth_CI(i)$meth_CI_C[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_C <- c(CI_upper_C, meth_CI(i)$meth_CI_C[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_CZ <- c(CI_lower_CZ, meth_CI(i)$meth_CI_CZ[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_CZ <- c(CI_upper_CZ, meth_CI(i)$meth_CI_CZ[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_phi <- c(CI_lower_phi, meth_CI(i)$meth_CI_phi[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_phi <- c(CI_upper_phi, meth_CI(i)$meth_CI_phi[[1]][2])
}
for (i in drugs_inference_sorted) {
  CI_lower_phiZ <- c(CI_lower_phiZ, meth_CI(i)$meth_CI_phiZ[[1]][1])
}
for (i in drugs_inference_sorted) {
  CI_upper_phiZ <- c(CI_upper_phiZ, meth_CI(i)$meth_CI_phiZ[[1]][2])
}
# Need to omit the first entry (NA)
Q_est <- as.numeric(na.omit(Q_est))
C_est <- as.numeric(na.omit(C_est))
Phi_est <- as.numeric(na.omit(Phi_est))
CI_lower_Q <- as.numeric(na.omit(CI_lower_Q))
CI_upper_Q <- as.numeric(na.omit(CI_upper_Q))
CI_lower_QZ <- as.numeric(na.omit(CI_lower_QZ))
CI_upper_QZ <- as.numeric(na.omit(CI_upper_QZ))
CI_lower_C <- as.numeric(na.omit(CI_lower_C))
CI_upper_C <- as.numeric(na.omit(CI_upper_C))
CI_lower_CZ <- as.numeric(na.omit(CI_lower_CZ))
CI_upper_CZ <- as.numeric(na.omit(CI_upper_CZ))
CI_lower_phi <- as.numeric(na.omit(CI_lower_phi))
CI_upper_phi <- as.numeric(na.omit(CI_upper_phi))
CI_lower_phiZ <- as.numeric(na.omit(CI_lower_phiZ))
CI_upper_phiZ <- as.numeric(na.omit(CI_upper_phiZ))

data_Q <- data.frame(drugs = fct_inorder(drugs_inference_sorted),
                   Q_est = Q_est,
                   C_est = C_est,
                   Phi_est = Phi_est,
                   CI_lower_Q = CI_lower_Q,
                   CI_upper_Q = CI_upper_Q,
                   CI_lower_QZ = CI_lower_QZ,
                   CI_upper_QZ = CI_upper_QZ,
                   CI_lower_C = CI_lower_C,
                   CI_upper_C = CI_upper_C,
                   CI_lower_CZ = CI_lower_CZ,
                   CI_upper_CZ = CI_upper_CZ,
                   CI_lower_phi = CI_lower_phi,
                   CI_upper_phi = CI_upper_phi,
                   CI_lower_phiZ = CI_lower_phiZ,
                   CI_upper_phiZ = CI_upper_phiZ)
options(ggplot2.discrete.colour= c("blue", "red"))
ggplot(data_Q, aes(drugs, Q_est)) +
    geom_errorbar(aes(ymin = CI_lower_Q, ymax = CI_upper_Q, color = "Standard-CIs"), linewidth = 0.8, width = 0.33, position = position_nudge(x = 0.2)) +
    geom_errorbar(aes(ymin = CI_lower_QZ, ymax = CI_upper_QZ, color = "Fisher-CIs"), linewidth = 0.8, width = 0.3, position = position_nudge(x = 0.2)) +
    geom_errorbar(aes(ymin = CI_lower_C, ymax = CI_upper_C, color = "Standard-CIs"), linewidth = 0.8, width = 0.3, position = position_nudge(x = -0.2)) +
    geom_errorbar(aes(ymin = CI_lower_CZ, ymax = CI_upper_CZ, color = "Fisher-CIs"), linewidth = 0.8, width = 0.3, position = position_nudge(x = -0.2)) +
    geom_errorbar(aes(ymin = CI_lower_phi, ymax = CI_upper_phi, color = "Standard-CIs"), linewidth = 0.8, width = 0.3) +
    geom_errorbar(aes(ymin = CI_lower_phiZ, ymax = CI_upper_phiZ, color = "Fisher-CIs"), linewidth = 0.8, width = 0.3) +
    geom_point(aes(drugs, Q_est, shape = "Q"), size = 3, position = position_nudge(x = 0.2)) +
    geom_point(aes(drugs, C_est, shape = "C"), size = 3, position = position_nudge(x = -0.2)) +
    geom_point(aes(drugs, Phi_est, shape = "\u03D5"), size = 3) +
    labs(x = "Drugs",
         y = "Cole's C, Phi Coefficient, Yule's Q") +
    geom_hline(yintercept = c(0,1), linetype = "dashed", color = "grey", alpha = 0.5) +
    geom_vline(xintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5, 10.5, 11.5, 12.5), color = "grey", alpha = 0.5) +
    theme_classic(base_size = 15) + 
    theme(legend.text = element_text(size=15), legend.position = "bottom", axis.title=element_text(size=15)) +
    scale_colour_manual(values = c("blue", "red")) +
    scale_shape_manual(values = c(15, 16, 17)) +
    scale_colour_discrete(name = "") +
    scale_shape_discrete(name = "", breaks = c("C", "\u03D5", "Q")) +
    ylim(0,1.06)


ggsave(filename = here("application/plots/QCPhi_application_inference_meth.pdf"), height = 200, width = (1+sqrt(5))/2*200, device = cairo_pdf, units = "mm")


```

```{r}
# Same figure as above but only with Fisher-CIs
options(ggplot2.discrete.colour= c("blue", "red", "green4"))
ggplot(data_Q, aes(drugs, Q_est)) +
    geom_errorbar(aes(ymin = CI_lower_QZ, ymax = CI_upper_QZ), color = "black", linewidth = 0.7, width = 0.3, position = position_nudge(x = 0.2)) +
    geom_errorbar(aes(ymin = CI_lower_CZ, ymax = CI_upper_CZ), color = "black", linewidth = 0.7, width = 0.3, position = position_nudge(x = -0.2)) +
    geom_errorbar(aes(ymin = CI_lower_phiZ, ymax = CI_upper_phiZ), color = "black", linewidth = 0.7, width = 0.3) +
    geom_point(aes(drugs, Q_est, shape = "Q", color = "Q"), size = 3, position = position_nudge(x = 0.2)) +
    geom_point(aes(drugs, C_est, shape = "C", color = "C"), size = 3, position = position_nudge(x = -0.2)) +
    geom_point(aes(drugs, Phi_est, shape = "\u03D5", color = "\u03D5"), size = 3) +
    labs(x = "Drugs",
         y = "Cole's C, Phi Coefficient, Yule's Q") +
    geom_hline(yintercept = c(0,1), linetype = "dashed", color = "grey", alpha = 0.5) +
    geom_vline(xintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5, 10.5, 11.5, 12.5), color = "grey", alpha = 0.5) +
    theme_classic(base_size = 15) + 
    theme(legend.text = element_text(size=15), legend.position = "bottom", axis.title=element_text(size=15)) +
    scale_colour_manual(values = c("blue", "red")) +
    scale_shape_manual(values = c(15, 16, 17)) +
    scale_colour_discrete(name = "", breaks = c("C", "\u03D5", "Q")) +
    scale_shape_discrete(name = "", breaks = c("C", "\u03D5", "Q")) +
    ylim(0,1.06)


ggsave(filename = here("application/plots/QCPhi_application_inference_meth_final.pdf"), height = 200, width = (1+sqrt(5))/2*200, device = cairo_pdf, units = "mm")
```

